---
title: "Bootstrapping"
author: "Mohsen rafiei"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE}
# This is a quick and casual analysis of our UX/HF dataset.
# Let's load some libraries first.
library(tidyverse)

# Load the dataset (assuming it's in the same folder as this Rmd file)
data <- read.csv("ux_hf_sample_data.csv")

# Take a quick look at the data
head(data)
summary(data)

# Cleaning and preprocessing the data
data <- data %>%
  mutate(
    Gender = as.factor(Gender), # Converting Gender to a factor
    Stress_Level = as.numeric(Stress_Level) # Ensuring Stress_Level is numeric
  )

# Check for missing values
if (any(is.na(data))) {
  print("Oops, there are missing values. Let's fix them.")
} else {
  print("Data looks clean. Moving on!")
}

# Basic analysis: Calculating averages
avg_time <- mean(data$Task_Completion_Time)
avg_accuracy <- mean(data$Accuracy)
avg_stress <- mean(data$Stress_Level)

cat("Average task completion time:", round(avg_time, 2), "seconds\n")
cat("Average accuracy:", round(avg_accuracy, 2), "%\n")
cat("Average stress level:", round(avg_stress, 2), "/10\n")

# Visualizing the distribution of task completion time
ggplot(data, aes(x = Task_Completion_Time)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "black") +
  labs(title = "Task Completion Time Distribution", x = "Time (seconds)", y = "Count")

# Visualizing accuracy vs stress level
ggplot(data, aes(x = Stress_Level, y = Accuracy, color = Gender)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(title = "Accuracy vs Stress Level", x = "Stress Level (1-10)", y = "Accuracy (%)") +
  theme_minimal()

# Bootstrap analysis: Mean of task completion time
bootstrap_means <- replicate(1000, {
  sample_time <- sample(data$Task_Completion_Time, replace = TRUE)
  mean(sample_time)
})

# Plotting the bootstrap distribution
ggplot(data.frame(Mean_Time = bootstrap_means), aes(x = Mean_Time)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black") +
  labs(title = "Bootstrap Distribution of Task Completion Time", x = "Mean Time (seconds)", y = "Frequency") +
  theme_minimal()

# Confidence interval for the bootstrapped means
ci <- quantile(bootstrap_means, probs = c(0.025, 0.975))
cat("95% CI for task completion time mean:", round(ci[1], 2), "to", round(ci[2], 2), "seconds\n")

# That's it! Feel free to tweak the code for more analyses or visualizations.
